Light curves of the brightest stars in the Southern sky\\ seen by bRing

### 2023-03-17 src/tex/ms.tex
[showyourwork] overleaf sync

%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
\documentclass{aa}

@@

\begin{document} 
\authorrunning{Kenworthy et al.}
\titlerunning{Planetary collision afterglow}
   \title{The eclipse of ASASSN-21qj: A planetary collision afterglow\\ and transit of the resultant debris cloud}

   \title{Light curves of the brightest stars in the Southern sky seen by bRing}

>>>>

%\documentclass[referee]{aa} % for a referee version
\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass{aa}

@@

\begin{document} 
\authorrunning{Kenworthy et al.}
\titlerunning{Brightest southern star light curves}

   \title{Light curves of the brightest stars in the Southern sky\\ seen by bRing}
